---
title: "Insect Welfare"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: flatly
---

```{css, echo=FALSE}
/* ── Navbar ─────────────────────────────────────────────── */
.navbar {
  background-color: #1B4332 !important;
  border-color: #1B4332 !important;
}
.navbar-brand {
  color: white !important;
  font-weight: 700;
  font-size: 17px;
  letter-spacing: 0.4px;
}
.navbar-nav > li > a {
  color: rgba(255,255,255,0.85) !important;
  font-weight: 500;
}
.navbar-nav > li > a:hover,
.navbar-nav > li.active > a {
  color: white !important;
  background-color: rgba(255,255,255,0.12) !important;
}

/* ── Section headers ─────────────────────────────────────── */
.chart-title {
  font-size: 13px;
  font-weight: 600;
  color: #2D3748;
  letter-spacing: 0.2px;
}

/* ── Value boxes ─────────────────────────────────────────── */
.value-box .value {
  font-size: 28px;
  font-weight: 700;
}
.value-box .caption {
  font-size: 12px;
  font-weight: 500;
  text-transform: uppercase;
  letter-spacing: 0.5px;
}

/* ── General layout ─────────────────────────────────────── */
body {
  font-family: 'Segoe UI', Helvetica, Arial, sans-serif;
  background-color: #F7F9F7;
}
.chart-wrapper {
  border-radius: 6px;
}

/* ── Allow AI summary cards to expand freely ─────────────── */
.chart-stage {
  overflow-y: auto !important;
}
details.ai-expand[open] ~ details.ai-expand {
  margin-top: 8px;
}
```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(visNetwork)
library(igraph)
library(tidytext)
library(ggwordcloud)
library(viridis)
library(plotly)
library(RColorBrewer)
library(DT)

# ── Load data ──────────────────────────────────────────────
datos <- read_csv("Gallery_Library.csv") %>%
  mutate(ID_Articulo = row_number())

Members <- read_csv("Members.csv")

# ── Colour palette ─────────────────────────────────────────
col_primary   <- "#2D6A4F"   # dark green (general)
col_highlight <- "#F4A261"   # warm orange (spotlight areas)
col_accent    <- "#C44E52"   # red (authors)
col_light     <- "#74C69D"   # light green (community)

# ── Helper: count articles matching a topic regex ──────────
count_topic <- function(pattern) {
  datos %>%
    filter(!is.na(Topics)) %>%
    separate_rows(Topics, sep = ",") %>%
    mutate(Topics = str_trim(Topics)) %>%
    filter(str_detect(Topics, regex(pattern, ignore_case = TRUE))) %>%
    pull(ID_Articulo) %>%
    n_distinct()
}

# ── Summary stats ──────────────────────────────────────────
n_total        <- nrow(datos)
n_authors      <- datos %>%
  filter(!is.na(Authors)) %>%
  separate_rows(Authors, sep = ";") %>%
  mutate(Authors = str_trim(Authors)) %>%
  pull(Authors) %>% n_distinct()

year_range <- datos %>%
  filter(!is.na(`Publication Year`)) %>%
  summarise(r = paste(min(`Publication Year`), max(`Publication Year`), sep = "–")) %>%
  pull(r)

n_insecticides <- count_topic("insecticide|pesticide")
n_anesthetics  <- count_topic("anesthes|anaesthes")
n_agriculture  <- count_topic("farming|agriculture|food")

# ── Spotlight regex (reused across plots) ──────────────────
spotlight_regex <- "insecticide|pesticide|anesthes|anaesthes|farming|agriculture|food|general anesthesia|killing method"
```


Literature {data-icon="fa-book"}
=====================================

Row {data-height=120}
-----------------------------------------------------------------------

### Total Articles

```{r}
valueBox(n_total, icon = "fa-book", color = col_primary,
         caption = "Articles in Library")
```

### Unique Authors

```{r}
valueBox(n_authors, icon = "fa-users", color = col_primary,
         caption = "Unique Authors")
```

### Years Covered

```{r}
valueBox(year_range, icon = "fa-calendar", color = "#457B9D",
         caption = "Publication Range")
```

### Insecticides & Pesticides

```{r}
valueBox(paste0(n_insecticides, " articles"), icon = "fa-flask",
         color = col_highlight, caption = "Insecticides & Pesticides")
```

### Insect Anesthetics

```{r}
valueBox(paste0(n_anesthetics, " articles"), icon = "fa-medkit",
         color = col_highlight, caption = "Insect Anesthetics")
```

### Farming & Agriculture

```{r}
valueBox(paste0(n_agriculture, " articles"), icon = "fa-leaf",
         color = col_highlight, caption = "Farming & Agriculture")
```


Row {data-height=460}
-----------------------------------------------------------------------

### Top 15 Most Frequent Topics {data-width=600}

```{r}
df_temas <- datos %>%
  filter(!is.na(Topics)) %>%
  separate_rows(Topics, sep = ",") %>%
  mutate(Topics = str_trim(Topics)) %>%
  filter(!str_detect(Topics, "Article Type")) %>%
  count(Topics, sort = TRUE) %>%
  slice_max(order_by = n, n = 15) %>%
  arrange(n) %>%
  mutate(
    Topics = factor(Topics, levels = Topics),
    Group  = if_else(
      str_detect(as.character(Topics), regex(spotlight_regex, ignore_case = TRUE)),
      "Key Research Area", "Other"
    )
  )

plot_ly() %>%
  add_bars(
    data        = filter(df_temas, Group == "Other"),
    x           = ~n, y = ~Topics, orientation = "h",
    name        = "Other",
    marker      = list(color = col_primary, opacity = 0.9),
    text        = ~paste0("<b>", Topics, "</b><br>Articles: ", n),
    hoverinfo   = "text"
  ) %>%
  add_bars(
    data        = filter(df_temas, Group == "Key Research Area"),
    x           = ~n, y = ~Topics, orientation = "h",
    name        = "Key Research Area",
    marker      = list(color = col_highlight, opacity = 0.9),
    text        = ~paste0("<b>", Topics, "</b><br>Articles: ", n),
    hoverinfo   = "text"
  ) %>%
  layout(
    xaxis   = list(title = "Number of Articles"),
    yaxis   = list(title = "", categoryorder = "total ascending"),
    legend  = list(orientation = "h", x = 0, y = -0.15),
    barmode = "overlay"
  )
```

### Word Cloud of Article Titles {data-width=400}

```{r}
data("stop_words")

datos %>%
  filter(!is.na(Title)) %>%
  unnest_tokens(word, Title) %>%
  anti_join(stop_words, by = "word") %>%
  filter(
    !word %in% c("evaluation", "effects", "effect", "study", "studies"),
    !str_detect(word, "^[0-9]+$")
  ) %>%
  mutate(word = case_when(
    word %in% c("animal", "animals")                            ~ "animals",
    word %in% c("insect", "insects")                            ~ "insects",
    word %in% c("invertebrate", "invertebrates")                ~ "invertebrates",
    word %in% c("anesthesia", "anesthetics", "anesthetic",
                "anaesthesia", "anaesthetics", "anaesthetic")   ~ "anesthesia",
    TRUE ~ word
  )) %>%
  count(word, sort = TRUE) %>%
  slice_max(order_by = n, n = 50) %>%
  ggplot(aes(label = word, size = n, color = n)) +
  geom_text_wordcloud_area(shape = "circle") +
  scale_size_area(max_size = 20) +
  scale_color_gradient(low = col_primary, high = col_highlight) +
  theme_minimal()
```


Row {data-height=420}
-----------------------------------------------------------------------

### Evolution of Publications per Year {data-width=500}

```{r}
df_years <- datos %>%
  filter(!is.na(`Publication Year`)) %>%
  count(`Publication Year`)

plot_ly(df_years,
  x          = ~`Publication Year`, y = ~n,
  type       = "bar",
  marker     = list(color = col_primary, opacity = 0.85),
  text       = ~paste0("Year: ", `Publication Year`, "<br>Articles: ", n),
  hoverinfo  = "text",
  showlegend = FALSE
) %>%
  layout(
    xaxis = list(title = "Year"),
    yaxis = list(title = "Number of Publications")
  )
```

### Article Types Over Time {data-width=500}

```{r}
df_types <- datos %>%
  filter(!is.na(Topics), !is.na(`Publication Year`)) %>%
  separate_rows(Topics, sep = ",") %>%
  mutate(Topics = str_trim(Topics)) %>%
  filter(str_detect(Topics, "Article Type")) %>%
  mutate(Topics = str_remove(Topics, "Article Type - ")) %>%
  mutate(Topics = fct_lump(Topics, n = 5)) %>%
  filter(Topics != "Other") %>%
  count(`Publication Year`, Topics)

type_levels <- levels(fct_lump(
  datos %>% filter(!is.na(Topics)) %>%
    separate_rows(Topics, sep = ",") %>%
    mutate(Topics = str_trim(Topics)) %>%
    filter(str_detect(Topics, "Article Type")) %>%
    mutate(Topics = str_remove(Topics, "Article Type - ")) %>%
    pull(Topics),
  n = 5
))
type_levels <- setdiff(type_levels, "Other")
pal_types   <- viridis::plasma(length(type_levels))

p_types <- plot_ly()
for (i in seq_along(type_levels)) {
  d <- df_types %>% filter(as.character(Topics) == type_levels[i])
  p_types <- p_types %>% add_bars(
    data      = d,
    x         = ~`Publication Year`, y = ~n,
    name      = type_levels[i],
    marker    = list(color = pal_types[i]),
    text      = ~paste0(Topics, "<br>Year: ", `Publication Year`, "<br>Articles: ", n),
    hoverinfo = "text"
  )
}
p_types %>% layout(
  barmode = "stack",
  xaxis   = list(title = "Year"),
  yaxis   = list(title = "Articles"),
  legend  = list(orientation = "h", x = 0, y = -0.2)
)
```


Row {data-height=430}
-----------------------------------------------------------------------

### Spotlight: Key Research Areas Over Time {data-width=500}

```{r}
df_spotlight <- datos %>%
  filter(!is.na(Topics), !is.na(`Publication Year`)) %>%
  separate_rows(Topics, sep = ",") %>%
  mutate(Topics = str_trim(Topics)) %>%
  mutate(Area = case_when(
    str_detect(Topics, regex("insecticide|pesticide",    ignore_case = TRUE)) ~ "Insecticides & Pesticides",
    str_detect(Topics, regex("anesthes|anaesthes",       ignore_case = TRUE)) ~ "Insect Anesthetics",
    str_detect(Topics, regex("farming|agriculture|food", ignore_case = TRUE)) ~ "Farming & Agriculture",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(Area)) %>%
  distinct(ID_Articulo, `Publication Year`, Area) %>%
  count(`Publication Year`, Area)

spotlight_cols <- c(
  "Insecticides & Pesticides" = "#E76F51",
  "Insect Anesthetics"        = "#F4A261",
  "Farming & Agriculture"     = col_primary
)

p_spotlight <- plot_ly()
for (a in names(spotlight_cols)) {
  d <- df_spotlight %>% filter(Area == a)
  p_spotlight <- p_spotlight %>% add_trace(
    data      = d,
    x         = ~`Publication Year`, y = ~n,
    type      = "scatter", mode = "lines+markers",
    name      = a,
    line      = list(color = spotlight_cols[a], width = 2.5),
    marker    = list(color = spotlight_cols[a], size = 8),
    text      = ~paste0(Area, "<br>Year: ", `Publication Year`, "<br>Articles: ", n),
    hoverinfo = "text"
  )
}
p_spotlight %>% layout(
  xaxis  = list(title = "Year"),
  yaxis  = list(title = "Articles"),
  legend = list(orientation = "h", x = 0, y = -0.2)
)
```

### Evolution of Top 5 Research Topics {data-width=500}

```{r}
top_temas <- datos %>%
  filter(!is.na(Topics)) %>%
  separate_rows(Topics, sep = ",") %>%
  mutate(Topics = str_trim(Topics)) %>%
  filter(!str_detect(Topics, "Article Type"), Topics != "Invertebrate") %>%
  count(Topics, sort = TRUE) %>%
  slice_max(order_by = n, n = 5) %>%
  pull(Topics)

df_top5 <- datos %>%
  filter(!is.na(`Publication Year`), !is.na(Topics)) %>%
  separate_rows(Topics, sep = ",") %>%
  mutate(Topics = str_trim(Topics)) %>%
  filter(Topics %in% top_temas) %>%
  count(`Publication Year`, Topics)

top5_cols <- RColorBrewer::brewer.pal(min(length(top_temas), 8), "Set1")[seq_along(top_temas)]
names(top5_cols) <- top_temas

p_top5 <- plot_ly()
for (i in seq_along(top_temas)) {
  d <- df_top5 %>% filter(Topics == top_temas[i])
  p_top5 <- p_top5 %>% add_trace(
    data      = d,
    x         = ~`Publication Year`, y = ~n,
    type      = "scatter", mode = "lines+markers",
    name      = top_temas[i],
    line      = list(color = top5_cols[i], width = 2),
    marker    = list(color = top5_cols[i], size = 7),
    text      = ~paste0(Topics, "<br>Year: ", `Publication Year`, "<br>Articles: ", n),
    hoverinfo = "text"
  )
}
p_top5 %>% layout(
  xaxis  = list(title = "Year"),
  yaxis  = list(title = "Articles"),
  legend = list(orientation = "h", x = 0, y = -0.2)
)
```


Row {data-height=420}
-----------------------------------------------------------------------

### Most Prolific Authors

```{r}
df_authors <- datos %>%
  filter(!is.na(Authors)) %>%
  separate_rows(Authors, sep = ";") %>%
  mutate(Authors = str_trim(Authors)) %>%
  count(Authors, sort = TRUE) %>%
  slice_max(order_by = n, n = 15) %>%
  arrange(n) %>%
  mutate(Authors = factor(Authors, levels = Authors))

plot_ly(df_authors,
  x           = ~n, y = ~Authors, orientation = "h",
  type        = "bar",
  marker      = list(color = col_accent, opacity = 0.85),
  text        = ~paste0(Authors, "<br>Articles: ", n),
  hoverinfo   = "text",
  showlegend  = FALSE
) %>%
  layout(
    xaxis = list(title = "Number of Articles"),
    yaxis = list(title = "")
  )
```


Row {data-height=540}
-----------------------------------------------------------------------

### Researcher Co-authorship Network {data-width=500}

```{r}
autores_df <- datos %>%
  select(ID_Articulo, Authors) %>%
  filter(!is.na(Authors)) %>%
  separate_rows(Authors, sep = ";") %>%
  mutate(Authors = str_trim(Authors))

conteo_total_autores <- autores_df %>% count(Authors)

edges_autores <- autores_df %>%
  inner_join(autores_df, by = "ID_Articulo", relationship = "many-to-many") %>%
  filter(Authors.x < Authors.y) %>%
  count(Authors.x, Authors.y, name = "value") %>%
  rename(from = Authors.x, to = Authors.y) %>%
  mutate(title = paste0("<p><b>Collaborations:</b> ", value, "</p>"))

nombres_unicos_autores <- unique(c(edges_autores$from, edges_autores$to))

nodes_autores <- tibble(id = nombres_unicos_autores, label = nombres_unicos_autores) %>%
  left_join(conteo_total_autores, by = c("id" = "Authors")) %>%
  mutate(
    title     = paste0("<p><b>Author:</b> ", id, "<br><b>Total articles:</b> ", n, "</p>"),
    color     = if_else(id %in% c("Fischer, Bob", "Barrett, Meghan"), "#FFD700", col_primary),
    size      = if_else(id %in% c("Fischer, Bob", "Barrett, Meghan"), 35, 20),
    font.size = if_else(id %in% c("Fischer, Bob", "Barrett, Meghan"), 20, 14)
  )

visNetwork(nodes_autores, edges_autores) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(color = list(color = "darkgray", highlight = "black"), smooth = FALSE) %>%
  visNodes(
    font   = list(color = "black", strokeWidth = 2, strokeColor = "white"),
    shadow = list(enabled = TRUE, size = 10)
  ) %>%
  visOptions(
    highlightNearest = list(enabled = TRUE, degree = 1, hover = TRUE),
    nodesIdSelection = TRUE
  ) %>%
  visInteraction(dragNodes = TRUE, dragView = TRUE, zoomView = TRUE, hover = TRUE)
```

### Topic Co-occurrence Network {data-width=500}

```{r}
temas_df <- datos %>%
  select(ID_Articulo, Topics) %>%
  filter(!is.na(Topics)) %>%
  separate_rows(Topics, sep = ",") %>%
  mutate(Topics = str_trim(Topics)) %>%
  filter(!str_detect(Topics, "Article Type"))

temas_frecuentes <- temas_df %>% count(Topics) %>% filter(n >= 3) %>% pull(Topics)

edges_temas <- temas_df %>%
  filter(Topics %in% temas_frecuentes) %>%
  inner_join(
    temas_df %>% filter(Topics %in% temas_frecuentes),
    by = "ID_Articulo", relationship = "many-to-many"
  ) %>%
  filter(Topics.x < Topics.y) %>%
  count(Topics.x, Topics.y, name = "value") %>%
  rename(from = Topics.x, to = Topics.y) %>%
  mutate(title = paste0("<p><b>Appeared together:</b> ", value, " times</p>"))

conteo_temas  <- temas_df %>% count(Topics)
nombres_temas <- unique(c(edges_temas$from, edges_temas$to))

nodes_temas <- tibble(id = nombres_temas, label = nombres_temas) %>%
  left_join(conteo_temas, by = c("id" = "Topics")) %>%
  mutate(
    title = paste0("<p><b>Topic:</b> ", id, "<br><b>Total articles:</b> ", n, "</p>"),
    value = n,
    color = if_else(
      str_detect(id, regex(spotlight_regex, ignore_case = TRUE)),
      col_highlight, col_primary
    )
  )

visNetwork(nodes_temas, edges_temas) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(color = list(color = "lightgray", highlight = "black")) %>%
  visNodes(
    font   = list(color = "black", strokeWidth = 1.5, strokeColor = "white"),
    shadow = list(enabled = TRUE, size = 10)
  ) %>%
  visOptions(
    highlightNearest = list(enabled = TRUE, degree = 1, hover = TRUE),
    nodesIdSelection = TRUE
  ) %>%
  visInteraction(dragNodes = TRUE, dragView = TRUE, zoomView = TRUE, hover = TRUE)
```


Row {data-height=50}
-----------------------------------------------------------------------

<div style="padding:8px 16px; background:#1B4332; color:white; font-size:13px; font-weight:600; border-radius:6px; letter-spacing:0.3px;">
  📍 Research Landscape — Where is the field concentrating, and where are the gaps?
</div>

Row {data-height=440}
-----------------------------------------------------------------------

### Welfare Criteria Coverage {data-width=550}

```{r}
# Welfare-specific terms that map to the presentation's key criteria
welfare_terms <- tibble(
  term    = c("Sentience", "Pain", "Nociception", "Consciousness",
              "Cognition", "Affective", "Stress", "Emotion",
              "Welfare", "Moral Status", "Learning", "Memory"),
  label   = c("Sentience", "Pain", "Nociception", "Consciousness",
              "Cognition", "Affective States", "Stress / Physiological",
              "Emotion", "Welfare (general)", "Moral Status",
              "Learning", "Memory")
)

df_welfare <- welfare_terms %>%
  mutate(
    n = map_int(term, function(t) {
      sum(str_detect(datos$Topics, regex(t, ignore_case = TRUE)), na.rm = TRUE)
    }),
    Gap = if_else(n <= 5, "Under-researched", "Established"),
    label = factor(label, levels = label[order(n)])
  ) %>%
  arrange(n) %>%
  mutate(label = factor(label, levels = label))

plot_ly(df_welfare,
  x           = ~n,
  y           = ~label,
  orientation = "h",
  type        = "bar",
  color       = ~Gap,
  colors      = c("Under-researched" = col_accent, "Established" = col_primary),
  opacity     = 0.88,
  text        = ~paste0(label, "<br>Articles: ", n, "<br><b>", Gap, "</b>"),
  hoverinfo   = "text"
) %>%
  layout(
    xaxis     = list(title = "Number of Articles"),
    yaxis     = list(title = ""),
    legend    = list(title = list(text = "<b>Coverage</b>"), orientation = "h",
                     x = 0.3, y = -0.15),
    barmode   = "overlay",
    shapes    = list(list(
      type    = "line", x0 = 5, x1 = 5, y0 = -0.5, y1 = nrow(df_welfare) - 0.5,
      line    = list(color = col_accent, width = 1.5, dash = "dot")
    )),
    annotations = list(list(
      x = 5.5, y = nrow(df_welfare) - 0.8, text = "gap threshold",
      showarrow = FALSE, font = list(size = 10, color = col_accent), xanchor = "left"
    ))
  )
```

### Study Design Balance {data-width=450}

```{r}
# Extract article types and map to meaningful design categories
df_design <- datos %>%
  filter(!is.na(Topics)) %>%
  separate_rows(Topics, sep = ",") %>%
  mutate(Topics = str_trim(Topics)) %>%
  filter(str_detect(Topics, "Article Type")) %>%
  mutate(Design = str_remove(Topics, "Article Type\\s*-\\s*") %>% str_trim()) %>%
  count(Design, sort = TRUE) %>%
  mutate(
    Category = case_when(
      str_detect(Design, regex("empirical|experimental|field|lab", ignore_case = TRUE)) ~ "Empirical",
      str_detect(Design, regex("review|meta|systematic", ignore_case = TRUE))           ~ "Review / Meta-analysis",
      str_detect(Design, regex("book|chapter|opinion|comment|editorial", ignore_case = TRUE)) ~ "Book / Opinion",
      TRUE ~ "Theoretical / Other"
    )
  ) %>%
  group_by(Category) %>%
  summarise(n = sum(n), .groups = "drop") %>%
  arrange(desc(n))

category_colors <- c(
  "Empirical"             = col_primary,
  "Review / Meta-analysis"= col_highlight,
  "Book / Opinion"        = "#A8DADC",
  "Theoretical / Other"   = "#E0E0E0"
)

plot_ly(df_design,
  labels  = ~Category,
  values  = ~n,
  type    = "pie",
  hole    = 0.52,
  marker  = list(
    colors = category_colors[df_design$Category],
    line   = list(color = "white", width = 2)
  ),
  textinfo      = "label+percent",
  hovertemplate = "<b>%{label}</b><br>Articles: %{value}<br>%{percent}<extra></extra>",
  showlegend    = TRUE
) %>%
  layout(
    legend      = list(orientation = "h", x = 0.1, y = -0.1),
    annotations = list(list(
      text      = paste0("<b>", sum(df_design$n), "</b><br>articles"),
      x = 0.5, y = 0.5, showarrow = FALSE,
      font      = list(size = 14, color = "#1B4332")
    ))
  )
```


Row {data-height=38}
-----------------------------------------------------------------------

<div style="padding:6px 16px; font-size:11.5px; color:#888; border-top:1px solid #e2e8f0; display:flex; justify-content:space-between; flex-wrap:wrap; gap:4px; align-items:center;">
  <span>📚 Data source: <a href="https://www.insectwelfare.com/research-library" target="_blank" style="color:#2D6A4F; text-decoration:none; font-weight:600;">IWRS Research Library</a> — Insect Welfare Research Society</span>
  <span>💻 Dashboard: <strong style="color:#2D3748;">Solimary García-Hernández</strong> · <a href="mailto:solimarygarcia@gmail.com" style="color:#2D6A4F; text-decoration:none;">solimarygarcia@gmail.com</a> · <em style="color:#aaa;">Built with AI assistance (Claude Code · Anthropic)</em></span>
</div>

Community {data-icon="fa-globe"}
=====================================

Row {data-height=120}
-----------------------------------------------------------------------

### Total Members

```{r}
valueBox(nrow(Members), icon = "fa-users", color = col_primary,
         caption = "Registered Members")
```

### Countries Represented

```{r}
valueBox(
  Members %>% mutate(Country = str_trim(Country)) %>% pull(Country) %>% n_distinct(na.rm = TRUE),
  icon    = "fa-globe",
  color   = "#457B9D",
  caption = "Countries"
)
```

### Disciplines

```{r}
valueBox(
  Members %>% filter(!is.na(`General Discipline`), `General Discipline` != "") %>%
    pull(`General Discipline`) %>% n_distinct(),
  icon    = "fa-university",
  color   = col_light,
  caption = "Research Disciplines"
)
```


Row {data-height=560}
-----------------------------------------------------------------------

### Global Member Map

```{r}
datos_mapa <- Members %>%
  mutate(Country = str_trim(Country)) %>%
  group_by(Country) %>%
  summarise(
    Total         = n(),
    Lista_Nombres = paste(head(paste(`First Name`, `Last Name`), 15), collapse = "<br>"),
    .groups       = "drop"
  ) %>%
  mutate(
    Lista_Nombres = if_else(
      Total > 15,
      paste0(Lista_Nombres, "<br><i>...and ", Total - 15, " more</i>"),
      Lista_Nombres
    ),
    Texto_Hover = paste0(
      "<b>", Country, "</b><br>",
      "<b>Members:</b> ", Total, "<br>",
      "─────────────────<br>",
      Lista_Nombres
    )
  )

plot_geo(datos_mapa) %>%
  add_trace(
    z            = ~Total,
    locations    = ~Country,
    locationmode = "country names",
    text         = ~Texto_Hover,
    hoverinfo    = "text",
    colorscale   = list(
      c(0,   "#D8F3DC"),
      c(0.4, "#52B788"),
      c(1,   "#1B4332")
    ),
    marker = list(line = list(color = toRGB("white"), width = 0.5))
  ) %>%
  colorbar(title = "Members") %>%
  layout(
    geo = list(
      showframe      = FALSE,
      showcoastlines = FALSE,
      showland       = TRUE,
      landcolor      = toRGB("#E8F4EA"),
      showocean      = TRUE,
      oceancolor     = toRGB("#EBF5FB"),
      projection     = list(type = "natural earth")
    ),
    paper_bgcolor = "rgba(0,0,0,0)",
    plot_bgcolor  = "rgba(0,0,0,0)"
  )
```


Row {data-height=420}
-----------------------------------------------------------------------

### Members by Country (Top 20) {data-width=400}

```{r}
df_country <- Members %>%
  mutate(Country = str_trim(Country)) %>%
  count(Country, sort = TRUE) %>%
  slice_max(order_by = n, n = 20) %>%
  arrange(n) %>%
  mutate(Country = factor(Country, levels = Country))

plot_ly(df_country,
  x           = ~n, y = ~Country, orientation = "h",
  type        = "bar",
  marker      = list(color = col_primary, opacity = 0.85),
  text        = ~paste0(Country, ": ", n, " members"),
  hoverinfo   = "text",
  showlegend  = FALSE
) %>%
  layout(
    xaxis = list(title = "Members"),
    yaxis = list(title = "")
  )
```

### Members by Discipline {data-width=400}

```{r}
df_disc <- Members %>%
  filter(!is.na(`General Discipline`), `General Discipline` != "") %>%
  mutate(Discipline = str_trim(`General Discipline`)) %>%
  mutate(Discipline = fct_lump(Discipline, n = 10)) %>%
  count(Discipline, sort = TRUE) %>%
  arrange(n) %>%
  mutate(Discipline = factor(Discipline, levels = Discipline))

plot_ly(df_disc,
  x           = ~n, y = ~Discipline, orientation = "h",
  type        = "bar",
  marker      = list(color = col_light, opacity = 0.85),
  text        = ~paste0(Discipline, ": ", n, " members"),
  hoverinfo   = "text",
  showlegend  = FALSE
) %>%
  layout(
    xaxis = list(title = "Members"),
    yaxis = list(title = "")
  )
```

### Members by Rank {data-width=300}

```{r}
df_rank <- Members %>%
  filter(!is.na(Rank), Rank != "") %>%
  count(Rank, sort = TRUE) %>%
  arrange(n) %>%
  mutate(Rank = factor(Rank, levels = Rank))

plot_ly(df_rank,
  x           = ~n, y = ~Rank, orientation = "h",
  type        = "bar",
  marker      = list(color = "#52B788", opacity = 0.85),
  text        = ~paste0(Rank, ": ", n, " members"),
  hoverinfo   = "text",
  showlegend  = FALSE
) %>%
  layout(
    xaxis = list(title = "Members"),
    yaxis = list(title = "")
  )
```


Row {data-height=38}
-----------------------------------------------------------------------

<div style="padding:6px 16px; font-size:11.5px; color:#888; border-top:1px solid #e2e8f0; display:flex; justify-content:space-between; flex-wrap:wrap; gap:4px; align-items:center;">
  <span>📚 Data source: <a href="https://www.insectwelfare.com/research-library" target="_blank" style="color:#2D6A4F; text-decoration:none; font-weight:600;">IWRS Research Library</a> — Insect Welfare Research Society</span>
  <span>💻 Dashboard: <strong style="color:#2D3748;">Solimary García-Hernández</strong> · <a href="mailto:solimarygarcia@gmail.com" style="color:#2D6A4F; text-decoration:none;">solimarygarcia@gmail.com</a> · <em style="color:#aaa;">Built with AI assistance (Claude Code · Anthropic)</em></span>
</div>

Fairer Fields {data-icon="fa-search"}
=====================================

```{r fairer-fields-data, include=FALSE}
# Articles matching key research areas
df_fairer <- datos %>%
  filter(!is.na(Topics)) %>%
  filter(str_detect(Topics, regex(spotlight_regex, ignore_case = TRUE))) %>%
  mutate(
    # Clickable DOI link
    DOI_link = if_else(
      !is.na(DOI) & DOI != "",
      paste0('<a href="', DOI, '" target="_blank">🔗 Open</a>'),
      "—"
    ),
    # Clean up Topics: remove "Article Type - " prefix for readability
    Topics_clean = str_replace_all(Topics, "Article Type - ", "") %>%
                   str_replace_all(",", " · "),
    # Tag which spotlight areas match
    Areas = case_when(
      str_detect(Topics, regex("insecticide|pesticide", ignore_case = TRUE)) &
        str_detect(Topics, regex("anesthes|anaesthes|general anesthesia|killing method", ignore_case = TRUE)) ~ "Insecticides · Anesthetics",
      str_detect(Topics, regex("insecticide|pesticide", ignore_case = TRUE)) ~ "Insecticides & Pesticides",
      str_detect(Topics, regex("anesthes|anaesthes|general anesthesia|killing method", ignore_case = TRUE)) ~ "Anesthetics / Killing Methods",
      str_detect(Topics, regex("farming|agriculture|food", ignore_case = TRUE)) ~ "Farming & Agriculture",
      TRUE ~ "Other"
    )
  ) %>%
  select(
    Title,
    Authors,
    Year      = `Publication Year`,
    Areas,
    Topics    = Topics_clean,
    DOI       = DOI_link
  )

# Demo article: first article with a non-empty Summary for the AI card
demo_article <- datos %>%
  filter(!is.na(Summary), Summary != "",
         str_detect(Topics, regex(spotlight_regex, ignore_case = TRUE))) %>%
  slice(1)

# If no article has a summary, fall back to any spotlight article
if (nrow(demo_article) == 0) {
  demo_article <- datos %>%
    filter(str_detect(Topics, regex(spotlight_regex, ignore_case = TRUE))) %>%
    slice(1)
}
```

Row {data-height=60}
-----------------------------------------------------------------------

<div style="padding: 10px 15px; background:#f0f7f2; border-left: 4px solid #2D6A4F; border-radius:4px; font-size:14px; color:#2D3748;">
  <b>Fairer Fields</b> — Articles from the library related to insecticides & pesticides, insect anesthetics, killing methods, and farming & agriculture. Use the search box and column filters to explore. <span style="color:#888;">Future feature: click any row to get an AI-generated summary.</span>
</div>

Row {data-height=500}
-----------------------------------------------------------------------

### Literature on Key Research Areas

```{r}
datatable(
  df_fairer,
  escape      = FALSE,          # render DOI as HTML link
  rownames    = FALSE,
  filter      = "top",          # per-column filters
  extensions  = "Buttons",
  options     = list(
    pageLength  = 15,
    dom         = "Bfrtip",
    buttons     = list(
      list(extend = "csv",   text = "Download CSV"),
      list(extend = "excel", text = "Download Excel")
    ),
    columnDefs  = list(
      list(width = "35%",  targets = 0),   # Title
      list(width = "20%",  targets = 1),   # Authors
      list(width = "5%",   targets = 2),   # Year
      list(width = "15%",  targets = 3),   # Areas
      list(width = "20%",  targets = 4),   # Topics
      list(width = "5%",   targets = 5)    # DOI
    ),
    scrollX     = TRUE
  ),
  class = "stripe hover compact"
) %>%
  formatStyle(
    "Areas",
    backgroundColor = styleEqual(
      c("Insecticides & Pesticides", "Anesthetics / Killing Methods",
        "Insecticides · Anesthetics", "Farming & Agriculture"),
      c("#fff3e0", "#e8f4fd", "#fce4d6", "#e8f5e9")
    ),
    fontWeight = "bold"
  )
```


Row {data-height=30}
-----------------------------------------------------------------------

<div style="padding:6px 15px; font-size:13px; color:#888; font-style:italic;">
  ✨ <b>AI Summary Preview</b> — demonstration of a future feature. In the full version, each article will have an automatically generated structured summary.
</div>

Row
-----------------------------------------------------------------------

### AI-Generated Summary (Demo)

```{r}
htmltools::HTML('
<style>
  details.ai-expand { margin-top:8px; }
  details.ai-expand summary {
    cursor:pointer; font-size:12px; font-weight:600; color:#2D6A4F;
    padding:7px 10px; background:#f0f7f2; border-radius:6px;
    list-style:none; display:flex; align-items:center; gap:6px;
    user-select:none;
  }
  details.ai-expand summary::-webkit-details-marker { display:none; }
  details.ai-expand summary::before { content:"▶"; font-size:9px; transition:transform 0.2s; }
  details.ai-expand[open] summary::before { content:"▶"; transform:rotate(90deg); display:inline-block; }
  details.ai-expand .detail-body {
    padding:10px 12px; font-size:12.5px; color:#2D3748; line-height:1.65;
    border-left:3px solid #74C69D; margin-top:6px; background:#fafafa; border-radius:0 6px 6px 0;
  }
  details.ai-expand .detail-body ul { margin:4px 0; padding-left:18px; }
  details.ai-expand .detail-body li { margin-bottom:4px; }
  details.ai-expand[data-type="results"] summary { color:#3730a3; background:#f0f4ff; }
  details.ai-expand[data-type="results"] .detail-body { border-left-color:#a5b4fc; }
  details.ai-expand[data-type="questions"] summary { color:#92400e; background:#fffbeb; }
  details.ai-expand[data-type="questions"] .detail-body { border-left-color:#fcd34d; }
</style>

<div style="font-family: Segoe UI, Helvetica, Arial, sans-serif; font-size:13.5px; line-height:1.6; display:grid; grid-template-columns:1fr 1fr; gap:16px;">

  <!-- ═══ Card 1: Lapied et al. ═══ -->
  <div style="background:white; border:1px solid #e2e8f0; border-radius:10px; padding:16px 18px; box-shadow:0 2px 8px rgba(0,0,0,0.05);">
    <div style="margin-bottom:10px;">
      <span style="background:#2D6A4F; color:white; border-radius:4px; padding:2px 8px; font-size:10.5px; font-weight:600; letter-spacing:0.5px;">AI SUMMARY · DEMO</span>
      <span style="margin-left:8px; background:#e8f5e9; color:#2D6A4F; border-radius:4px; padding:2px 7px; font-size:10.5px; font-weight:600;">Insecticides</span>
    </div>
    <div style="font-size:14px; font-weight:700; color:#1B4332; margin-bottom:2px; line-height:1.4;">Indoxacarb, an oxadiazine insecticide, blocks insect neuronal sodium channels</div>
    <div style="color:#888; font-size:12px; margin-bottom:12px;">Lapied et al. &middot; <em>British Journal of Pharmacology</em> &middot; 2001</div>

    <div style="display:grid; grid-template-columns:1fr 1fr 1fr; gap:10px; margin-bottom:4px;">
      <div style="background:#f0f7f2; border-radius:7px; padding:10px;">
        <div style="font-weight:700; color:#2D6A4F; font-size:11px; text-transform:uppercase; letter-spacing:0.5px; margin-bottom:5px;">🔬 Hypothesis</div>
        <div style="color:#2D3748; font-size:12.5px;">DCJW (active metabolite of indoxacarb) selectively blocks voltage-dependent Na⁺ channels in insect neurons via a binding site shared with local anesthetics, distinct from pyrethroids and TTX.</div>
      </div>
      <div style="background:#fff8f0; border-radius:7px; padding:10px;">
        <div style="font-weight:700; color:#c05621; font-size:11px; text-transform:uppercase; letter-spacing:0.5px; margin-bottom:5px;">⚗️ Experiments</div>
        <div style="color:#2D3748; font-size:12.5px;">Whole-cell patch-clamp on isolated cockroach (<em>Periplaneta americana</em>) DUM neurons; IC50 dose-response curves; co-application with TTX and lidocaine; Ca²⁺/K⁺ selectivity tests.</div>
      </div>
      <div style="background:#f0f4ff; border-radius:7px; padding:10px;">
        <div style="font-weight:700; color:#3730a3; font-size:11px; text-transform:uppercase; letter-spacing:0.5px; margin-bottom:5px;">📊 Results</div>
        <div style="color:#2D3748; font-size:12.5px;">IC50 = 28 nM; additive with TTX; competitive with lidocaine; no effect on Ca²⁺ or K⁺; membrane hyperpolarized from −53.5 to −72.5 mV.</div>
      </div>
    </div>

    <details class="ai-expand">
      <summary>🔬 Want to know more about the methodology?</summary>
      <div class="detail-body">
        <ul>
          <li>DUM (<em>dorsal unpaired median</em>) neurons enzymatically isolated from the terminal abdominal ganglia of <em>Periplaneta americana</em>.</li>
          <li><strong>Whole-cell patch-clamp</strong> in a superfusion chamber (~0.1 mL volume) at room temperature.</li>
          <li>DCJW applied via bath superfusion at concentrations ranging 1 nM to 10 µM; TTX used at 300 nM as a reference sodium channel blocker.</li>
          <li>Lidocaine tested at 1–30 mM for competitive co-application experiments.</li>
          <li>Ca²⁺ currents measured using Ba²⁺ as charge carrier; K⁺ currents isolated in Ca²⁺-free external solution.</li>
          <li>Membrane potential recorded in current-clamp mode; input resistance calculated from responses to hyperpolarizing current pulses.</li>
        </ul>
      </div>
    </details>

    <details class="ai-expand">
      <summary>⚗️ Want to know more about the statistical analyses?</summary>
      <div class="detail-body">
        <ul>
          <li>Concentration-response curves fitted with the <strong>Hill equation</strong> to derive IC50 and Hill coefficient.</li>
          <li>Current amplitudes normalized to pre-drug control peak values.</li>
          <li>DCJW + TTX combined inhibition analysed to test <strong>additivity vs. independence</strong> of binding sites.</li>
          <li>DCJW + lidocaine co-application tested for <strong>competitive interaction</strong>: combined effect significantly lower than additive expectation confirms shared binding site.</li>
          <li>Statistical comparisons by <strong>paired t-test</strong> (currents before vs. during drug application); p &lt; 0.05.</li>
          <li>Input resistance and resting membrane potential compared before and during DCJW superfusion.</li>
        </ul>
      </div>
    </details>

    <details class="ai-expand" data-type="results">
      <summary>📊 Want to know more about the main results?</summary>
      <div class="detail-body">
        <ul>
          <li><strong>IC50 = 28 nM</strong> for peak sodium current inhibition — 10× less potent than TTX, but ~1,000× more potent than lidocaine.</li>
          <li>DCJW + TTX combination produced <strong>additive inhibition</strong>, confirming they act at independent, non-overlapping binding sites.</li>
          <li>DCJW + lidocaine produced <strong>less-than-additive inhibition</strong>, confirming competitive binding at a shared site (local anesthetic receptor).</li>
          <li>No significant effect on Ca²⁺ or K⁺ currents at tested concentrations — <strong>high selectivity for Na⁺ channels</strong>.</li>
          <li>Resting membrane potential shifted from −53.5 mV to −72.5 mV (hyperpolarization); <strong>input resistance increased by ~41%</strong>.</li>
          <li>First mechanistic characterisation of indoxacarb action on insect neuronal sodium channels, providing a pharmacological basis distinct from all prior insecticide classes.</li>
        </ul>
      </div>
    </details>

    <details class="ai-expand" data-type="questions">
      <summary>💡 Open questions &amp; future directions</summary>
      <div class="detail-body">
        <ul>
          <li>Does DCJW affect other insect sodium channel subtypes (e.g., para-type variants expressed in sensory neurons)?</li>
          <li>Is the lidocaine-shared binding site conserved across beneficial insects — particularly bees (<em>Apis mellifera</em>) and other pollinators?</li>
          <li>What are the <strong>sublethal behavioural consequences</strong> of DCJW at environmentally relevant concentrations (below IC50)?</li>
          <li>Could this pharmacological target be exploited to design <strong>more selective</strong> insecticides with reduced off-target effects?</li>
          <li>How does resistance to indoxacarb evolve at the molecular level — are sodium channel mutations observed in resistant field populations?</li>
        </ul>
      </div>
    </details>
  </div>

  <!-- ═══ Card 2: Guo et al. ═══ -->
  <div style="background:white; border:1px solid #e2e8f0; border-radius:10px; padding:16px 18px; box-shadow:0 2px 8px rgba(0,0,0,0.05);">
    <div style="margin-bottom:10px;">
      <span style="background:#2D6A4F; color:white; border-radius:4px; padding:2px 8px; font-size:10.5px; font-weight:600; letter-spacing:0.5px;">AI SUMMARY · DEMO</span>
      <span style="margin-left:8px; background:#fff3e0; color:#e65100; border-radius:4px; padding:2px 7px; font-size:10.5px; font-weight:600;">Anesthetics · Insecticides</span>
    </div>
    <div style="font-size:14px; font-weight:700; color:#1B4332; margin-bottom:2px; line-height:1.4;">Convergent evolution of <em>Rdl</em> duplications as insect counter-defense against plant neurotoxins and synthetic insecticides</div>
    <div style="color:#888; font-size:12px; margin-bottom:12px;">Guo et al. &middot; <em>Nature Ecology &amp; Evolution</em> &middot; 2023</div>

    <div style="display:grid; grid-template-columns:1fr 1fr 1fr; gap:10px; margin-bottom:4px;">
      <div style="background:#f0f7f2; border-radius:7px; padding:10px;">
        <div style="font-weight:700; color:#2D6A4F; font-size:11px; text-transform:uppercase; letter-spacing:0.5px; margin-bottom:5px;">🔬 Hypothesis</div>
        <div style="color:#2D3748; font-size:12.5px;">Convergent amino acid substitutions in duplicated <em>Rdl</em> (GABA receptor gene) evolved over 300 Myr as a counter-defense against plant terpenoids — and the same changes rapidly re-emerged against synthetic insecticides.</div>
      </div>
      <div style="background:#fff8f0; border-radius:7px; padding:10px;">
        <div style="font-weight:700; color:#c05621; font-size:11px; text-transform:uppercase; letter-spacing:0.5px; margin-bottom:5px;">⚗️ Experiments</div>
        <div style="color:#2D3748; font-size:12.5px;">Phylogenetics (22 orders, 171 families); molecular docking; CRISPR-Cas9 in <em>Drosophila</em>; survival bioassays on picrotoxin/thymol; fitness cost assays; ancestral-state reconstruction.</div>
      </div>
      <div style="background:#f0f4ff; border-radius:7px; padding:10px;">
        <div style="font-weight:700; color:#3730a3; font-size:11px; text-transform:uppercase; letter-spacing:0.5px; margin-bottom:5px;">📊 Results</div>
        <div style="color:#2D3748; font-size:12.5px;">≥8 independent <em>Rdl</em> duplications; 2&prime; substitutions sterically block NCA binding; <em>Rdl</em> copy number explains 10–14% of diversification variance in Lepidoptera.</div>
      </div>
    </div>

    <details class="ai-expand">
      <summary>🔬 Want to know more about the methodology?</summary>
      <div class="detail-body">
        <ul>
          <li>Maximum-likelihood phylogenetic reconstruction across 411 species (22 insect orders, 171 families); <em>Rdl</em> gene copy number counted per genome.</li>
          <li>Homology models of the RDL receptor based on the <em>C. elegans</em> GluCl crystal structure; <strong>molecular docking</strong> with AutoDock Vina for picrotoxin and thymol.</li>
          <li><strong>CRISPR-Cas9</strong> editing in <em>Drosophila melanogaster</em> (w¹¹¹⁸ background): introduced substitutions A2&#39;S, A2&#39;Q, A2&#39;N, A2&#39;P and T6&#39;I at the 2&#39; pore-lining position.</li>
          <li>Survival bioassays: picrotoxin- and thymol-supplemented diets at increasing concentrations, tested in adults and larvae.</li>
          <li>Fitness cost assays: egg-laying rate, heat-induced paralysis (37 °C), and locomotor performance (climbing assay) across genotypes.</li>
        </ul>
      </div>
    </details>

    <details class="ai-expand">
      <summary>⚗️ Want to know more about the statistical analyses?</summary>
      <div class="detail-body">
        <ul>
          <li><strong>Ancestral-state reconstruction</strong> via stochastic character mapping to infer the origin of duplications and substitutions across the phylogeny.</li>
          <li>Sister-clade <strong>diversification rate comparison</strong> (BiSSE-like approach); Pearson correlation between <em>Rdl</em> copy number and net diversification rate.</li>
          <li>Docking scores compared between wild-type and mutant receptor models to quantify <strong>binding affinity reduction</strong> for picrotoxin/thymol.</li>
          <li>Survival analysed with <strong>logistic regression</strong>; S/S and Q/+ genotypes compared against controls.</li>
          <li>Fitness costs tested with <strong>Mann-Whitney U tests</strong>; Q/Q and P/P genotypes showed significantly reduced fecundity and increased heat-induced paralysis.</li>
        </ul>
      </div>
    </details>

    <details class="ai-expand" data-type="results">
      <summary>📊 Want to know more about the main results?</summary>
      <div class="detail-body">
        <ul>
          <li>Identified <strong>≥8 independent <em>Rdl</em> gene duplication events</strong> across insect lineages, distributed across Lepidoptera, Diptera, Coleoptera, and others.</li>
          <li>Substitutions at the <strong>2&prime; pore-lining position</strong> (A2&#39;S, A2&#39;Q) reduce pore radius, sterically blocking the binding of non-competitive antagonists (picrotoxin, thymol, fipronil).</li>
          <li>S/S and Q/+ genotypes showed <strong>significantly increased survival</strong> on both picrotoxin and thymol diets; P/P genotype was less effective.</li>
          <li><em>Rdl</em> copy number <strong>positively correlates with net diversification rate</strong> in Lepidoptera, explaining 10–14% of variance — suggesting a macroevolutionary advantage.</li>
          <li><strong>Fitness trade-offs</strong>: Q/Q homozygotes showed reduced egg-laying and higher heat-induced paralysis, suggesting the duplicate copy buffers fitness costs in heterozygotes.</li>
          <li>The same 2&prime; substitutions documented in <strong>field-collected resistant populations</strong> within one human lifetime — evolutionary parallel between deep evolutionary history and contemporary insecticide resistance.</li>
        </ul>
      </div>
    </details>

    <details class="ai-expand" data-type="questions">
      <summary>💡 Open questions &amp; future directions</summary>
      <div class="detail-body">
        <ul>
          <li>Do <em>Rdl</em> duplications provide resistance to <strong>other GABA-targeting insecticides</strong> (e.g., dieldrin, endosulfan) beyond fipronil and picrotoxin?</li>
          <li>Do similar convergent mechanisms occur in <strong>other receptor families</strong> (sodium channels, acetylcholinesterase) under plant-derived toxin pressure?</li>
          <li>Can <em>Rdl</em> copy number variation be used to <strong>predict resistance evolution</strong> in uncharacterised pest species before it emerges?</li>
          <li>How do <em>Rdl</em> duplications affect <strong>ecologically relevant interactions</strong> — e.g., competition, predator-prey dynamics in naturally terpenoid-rich environments?</li>
          <li>What are the <strong>welfare implications</strong> for insects whose GABA receptors are structurally altered — does insecticide action cause different pain/distress responses in resistant vs. susceptible individuals?</li>
        </ul>
      </div>
    </details>
  </div>

</div>
')
```


Row {data-height=38}
-----------------------------------------------------------------------

<div style="padding:6px 16px; font-size:11.5px; color:#888; border-top:1px solid #e2e8f0; display:flex; justify-content:space-between; flex-wrap:wrap; gap:4px; align-items:center;">
  <span>📚 Data source: <a href="https://www.insectwelfare.com/research-library" target="_blank" style="color:#2D6A4F; text-decoration:none; font-weight:600;">IWRS Research Library</a> — Insect Welfare Research Society</span>
  <span>💻 Dashboard: <strong style="color:#2D3748;">Solimary García-Hernández</strong> · <a href="mailto:solimarygarcia@gmail.com" style="color:#2D6A4F; text-decoration:none;">solimarygarcia@gmail.com</a> · <em style="color:#aaa;">Built with AI assistance (Claude Code · Anthropic)</em></span>
</div>

Cost-Effectiveness {data-icon="fa-calculator"}
=====================================

Row {data-height=780}
-----------------------------------------------------------------------

### Paying Farmers for Humane Pesticides — Interactive Simulator

```{=html}
<div id="welfare-sim" style="font-family:'Segoe UI',Helvetica,Arial,sans-serif; padding:6px 4px; font-size:13px;">

  <!-- Header banner -->
  <div style="background:#1B4332; color:white; padding:10px 16px; border-radius:8px; margin-bottom:14px; display:flex; align-items:center; justify-content:space-between; flex-wrap:wrap; gap:8px;">
    <div>
      <div style="font-size:15px; font-weight:700; margin-bottom:2px;">🌾 Welfare Cost-Effectiveness Simulator</div>
      <div style="font-size:11.5px; opacity:0.85;">How many insect death-experiences are prevented per dollar spent compensating farmers to switch to a more humane pesticide?</div>
    </div>
  </div>

  <!-- Explainer accordion -->
  <details style="margin-bottom:14px; border:1px solid #b7e4c7; border-radius:8px; overflow:hidden;">
    <summary style="cursor:pointer; background:#f0f7f2; padding:10px 16px; font-size:13px; font-weight:700; color:#1B4332; list-style:none; display:flex; align-items:center; gap:8px; user-select:none;">
      <span style="font-size:10px;">▶</span> 💡 What is this? &amp; How it works
    </summary>
    <div style="padding:14px 18px; font-size:12.5px; color:#2D3748; line-height:1.75; background:white;">

      <p style="margin:0 0 10px 0;"><strong>What is this?</strong><br>
      This interactive simulator estimates the cost-effectiveness of paying farmers to switch from a conventional pesticide to a more humane alternative — one that kills insects faster, reducing the total duration of suffering.</p>

      <p style="margin:0 0 8px 0;"><strong>How it works</strong><br>
      The model computes <strong>R</strong>, the expected number of insect death-experiences prevented per dollar spent on farmer compensation. R is driven by five parameters you control:</p>

      <ul style="margin:0 0 10px 0; padding-left:20px; line-height:1.9;">
        <li><strong>p</strong> — how likely you think insects can feel pain</li>
        <li><strong>n</strong> — how many insects live on a hectare of cropland</li>
        <li><strong>f</strong> — what fraction of those insects are killed by pesticide application</li>
        <li><strong>s</strong> — how much less painful the humane pesticide is relative to the current one</li>
        <li><strong>c</strong> — the extra cost per hectare of using the humane pesticide</li>
      </ul>

      <p style="margin:0 0 10px 0;">Adjust the sliders to reflect your own assumptions. The histogram shows the full range of plausible outcomes from 10,000 Monte Carlo simulations using the uncertainty ranges from the original model — your point estimate appears as a red line so you can see where your assumptions land relative to that distribution.</p>

      <p style="margin:0 0 10px 0;">The <strong>"What does this mean in practice?"</strong> section translates the result into plain farmer-scale numbers: how many insects are spared on a farm of your chosen size, what the subsidy would cost per season, and how much it costs to prevent 1,000 insects from unnecessary suffering.</p>

      <p style="margin:0; background:#f0f7f2; border-left:3px solid #2D6A4F; padding:8px 12px; border-radius:0 6px 6px 0;">
        <strong>Why does it matter?</strong> Even under conservative assumptions, the cost per unit of suffering prevented is remarkably low — suggesting that farmer subsidy programs targeting pesticide humaneness could be among the most cost-effective interventions in insect welfare.
      </p>

    </div>
  </details>

  <!-- Main two-column layout -->
  <div style="display:grid; grid-template-columns:300px 1fr; gap:14px; align-items:start;">

    <!-- ── LEFT: parameter sliders ── -->
    <div style="background:white; border:1px solid #e2e8f0; border-radius:10px; padding:16px;">
      <div style="display:flex; justify-content:space-between; align-items:center; margin-bottom:12px;">
        <div style="font-weight:700; font-size:11px; color:#1B4332; text-transform:uppercase; letter-spacing:0.6px;">📐 Set Your Parameters</div>
        <button onclick="wReset()" style="font-size:11px; font-weight:600; color:#2D6A4F; background:#f0f7f2; border:1px solid #b7e4c7; border-radius:5px; padding:3px 10px; cursor:pointer;">↺ Reset defaults</button>
      </div>

      <!-- p -->
      <div style="margin-bottom:13px;">
        <div style="display:flex; justify-content:space-between; margin-bottom:2px;">
          <span style="font-weight:600; color:#2D3748; font-size:12px;"><em>p</em> — Probability insects feel pain</span>
          <span id="lbl-p" style="font-weight:700; color:#2D6A4F; font-size:12px;">0.100</span>
        </div>
        <div style="font-size:11px; color:#888; margin-bottom:4px; line-height:1.4;">Your subjective belief that insects are sentient and capable of experiencing suffering. Likely varies by species; treated here as a single value across all insects.</div>
        <input type="range" id="sl-p" min="0.001" max="0.6" step="0.001" value="0.1"
               style="width:100%; accent-color:#2D6A4F;" oninput="wSim()">
        <div style="display:flex; justify-content:space-between; font-size:10px; color:#aaa; margin-top:1px;"><span>0.001 (very unlikely)</span><span>0.6 (quite likely)</span></div>
      </div>

      <!-- n -->
      <div style="margin-bottom:13px;">
        <div style="display:flex; justify-content:space-between; margin-bottom:2px;">
          <span style="font-weight:600; color:#2D3748; font-size:12px;"><em>n</em> — Insects per hectare</span>
          <span id="lbl-n" style="font-weight:700; color:#2D6A4F; font-size:12px;">3.3M</span>
        </div>
        <div style="font-size:11px; color:#888; margin-bottom:4px; line-height:1.4;">Average number of insects (and other small sentient organisms) inhabiting one hectare of cropland during the growing season. Varies widely by crop type and region.</div>
        <input type="range" id="sl-n" min="12" max="18" step="0.05" value="15"
               style="width:100%; accent-color:#2D6A4F;" oninput="wSim()">
        <div style="display:flex; justify-content:space-between; font-size:10px; color:#aaa; margin-top:1px;"><span>163K</span><span>65M</span></div>
      </div>

      <!-- f -->
      <div style="margin-bottom:13px;">
        <div style="display:flex; justify-content:space-between; margin-bottom:2px;">
          <span style="font-weight:600; color:#2D3748; font-size:12px;"><em>f</em> — Fraction killed by pesticide</span>
          <span id="lbl-f" style="font-weight:700; color:#2D6A4F; font-size:12px;">0.80</span>
        </div>
        <div style="font-size:11px; color:#888; margin-bottom:4px; line-height:1.4;">Proportion of insects on a treated hectare that are killed or significantly harmed by a single pesticide application. Assumes both pesticides are equally potent.</div>
        <input type="range" id="sl-f" min="0.05" max="1.0" step="0.01" value="0.8"
               style="width:100%; accent-color:#2D6A4F;" oninput="wSim()">
        <div style="display:flex; justify-content:space-between; font-size:10px; color:#aaa; margin-top:1px;"><span>0.05 (few affected)</span><span>1.0 (all killed)</span></div>
      </div>

      <!-- s -->
      <div style="margin-bottom:13px;">
        <div style="display:flex; justify-content:space-between; margin-bottom:2px;">
          <span style="font-weight:600; color:#2D3748; font-size:12px;"><em>s</em> — Painfulness ratio (humane / harmful)</span>
          <span id="lbl-s" style="font-weight:700; color:#2D6A4F; font-size:12px;">0.50 <span style="font-weight:400; color:#888;">(50% reduction)</span></span>
        </div>
        <div style="font-size:11px; color:#888; margin-bottom:4px; line-height:1.4;">How painful the humane pesticide is relative to the current one, per unit of time. E.g., s = 0.5 means the humane pesticide kills twice as fast, causing half the total suffering. Lower = greater welfare benefit.</div>
        <input type="range" id="sl-s" min="0.05" max="0.99" step="0.01" value="0.5"
               style="width:100%; accent-color:#2D6A4F;" oninput="wSim()">
        <div style="display:flex; justify-content:space-between; font-size:10px; color:#aaa; margin-top:1px;"><span>0.05 (95% less painful)</span><span>0.99 (1% less painful)</span></div>
      </div>

      <!-- c -->
      <div style="margin-bottom:14px;">
        <div style="display:flex; justify-content:space-between; margin-bottom:2px;">
          <span style="font-weight:600; color:#2D3748; font-size:12px;"><em>c</em> — Cost premium per hectare ($)</span>
          <span id="lbl-c" style="font-weight:700; color:#2D6A4F; font-size:12px;">$4.50</span>
        </div>
        <div style="font-size:11px; color:#888; margin-bottom:4px; line-height:1.4;">The extra cost per hectare of using the more humane pesticide instead of the current one. This is the amount a subsidy program would need to compensate farmers per hectare treated.</div>
        <input type="range" id="sl-c" min="1" max="300" step="1" value="4.5"
               style="width:100%; accent-color:#2D6A4F;" oninput="wSim()">
        <div style="display:flex; justify-content:space-between; font-size:10px; color:#aaa; margin-top:1px;"><span>$1</span><span>$300</span></div>
      </div>

    </div>

    <!-- ── RIGHT: results ── -->
    <div>

      <!-- Live formula -->
      <div style="background:#f0f7f2; border:1px solid #b7e4c7; border-radius:8px; padding:9px 14px; margin-bottom:13px; font-size:13px; color:#1B4332; display:flex; align-items:center; gap:8px; flex-wrap:wrap;">
        <span style="font-family:monospace;">R = p × n × f × (1−s) / c</span>
        <span style="color:#888; font-size:12px;">=</span>
        <span id="formula-live" style="font-weight:800; font-size:15px; color:#1B4332;">—</span>
        <span style="font-size:11px; color:#888;">death-experiences prevented per dollar</span>
      </div>

      <!-- Farmer translation card -->
      <div style="background:#fffdf5; border:1px solid #fde68a; border-radius:10px; padding:14px 16px; margin-bottom:13px;">
        <div style="display:flex; justify-content:space-between; align-items:center; margin-bottom:10px; flex-wrap:wrap; gap:8px;">
          <div style="font-weight:700; font-size:12px; color:#92400e;">🌾 What does this mean in practice?</div>
          <div style="display:flex; align-items:center; gap:6px; font-size:11.5px; color:#78350f;">
            <label for="sl-farm">Farm size:</label>
            <input type="number" id="sl-farm" value="50" min="1" max="50000" step="10"
              style="width:70px; font-size:12px; padding:2px 6px; border:1px solid #fcd34d; border-radius:4px; text-align:center;"
              oninput="wSim()">
            <span>hectares</span>
          </div>
        </div>
        <div id="farmer-text" style="font-size:12.5px; color:#44403c; line-height:1.8;"></div>
      </div>

      <!-- Histogram panel -->
      <div style="background:white; border:1px solid #e2e8f0; border-radius:10px; padding:14px;">
        <div style="font-size:14px; font-weight:700; color:#1B4332; margin-bottom:4px;">
          Given the uncertainty in these parameters, results can vary enormously — where do your assumptions land?
        </div>
        <div style="font-size:11px; color:#999; margin-bottom:8px;">
          R distribution · 50,000 Monte Carlo draws · log<sub>10</sub> scale &nbsp;|&nbsp;
          <span style="color:#C44E52; font-weight:600;">Red line</span> = your point estimate &nbsp;|&nbsp;
          <span style="color:#F4A261; font-weight:600;">Orange dashed</span> = MC mean
        </div>
        <svg id="hist-svg" style="width:100%; height:170px; display:block; overflow:visible;"></svg>
      </div>

      <!-- Histogram interpretation -->
      <div style="margin-top:12px; background:#f0f7f2; border:1px solid #b7e4c7; border-radius:8px; padding:12px 16px; font-size:12px; color:#2D3748; line-height:1.7;">
        <div style="font-weight:700; color:#1B4332; margin-bottom:6px;">📖 How to read this chart</div>
        <p style="margin:0 0 6px 0;">The x-axis shows <strong>R</strong> — the expected number of insect death-experiences prevented per dollar — on a <strong>logarithmic scale</strong> (powers of 10). Because the inputs are uncertain and span many orders of magnitude, the result can range from tens to hundreds of millions; a log scale makes the full distribution visible at once.</p>
        <p style="margin:0 0 6px 0;">The <strong>green bars</strong> are a Monte Carlo distribution: 50,000 simulations drawn randomly from the uncertainty ranges described in the original model (Brian Tomasik). Each bar shows how often R fell in that range — a tall bar means that outcome is more probable under those priors. Bars to the <em>left</em> of your red line are shaded lighter to help you see where your estimate sits relative to the distribution.</p>
        <p style="margin:0 0 6px 0;">The <span style="color:#C44E52; font-weight:700;">red vertical line</span> is <strong>your point estimate</strong> — the single value of R computed directly from your slider settings. If it falls near the center of the distribution, your assumptions are typical. If it falls in the tail, your assumptions are more optimistic or pessimistic than the model average.</p>
        <p style="margin:0 0 6px 0;">The <span style="color:#F4A261; font-weight:700;">orange dashed line</span> is the <strong>Monte Carlo mean</strong> — the average R across all 50,000 simulations using the original priors. Compare it to your red line to see how your assumptions differ from the model defaults.</p>
        <p style="margin:0; background:#fffbeb; border-left:3px solid #F4A261; padding:8px 12px; border-radius:0 6px 6px 0; font-size:11.5px;">
          <strong>If your red line is to the right of the orange:</strong> your assumptions are more optimistic than the model average — you believe the intervention prevents more suffering per dollar (e.g., you assigned a higher probability that insects feel pain, or assumed a larger insect population).<br>
          <strong>If your red line is to the left of the orange:</strong> your assumptions are more conservative — you expect fewer insects to benefit, or the cost premium is too high to make the intervention efficient under your values.
        </p>
      </div>

      <!-- Stat cards (below histogram) -->
      <div style="display:grid; grid-template-columns:1fr 1fr 1fr; gap:10px; margin-top:12px;">
        <div style="background:white; border:1px solid #e2e8f0; border-radius:8px; padding:12px; text-align:center;">
          <div style="font-size:10px; text-transform:uppercase; letter-spacing:0.5px; color:#888; margin-bottom:5px;">Expected R (point est.)</div>
          <div id="st-R" style="font-size:22px; font-weight:800; color:#2D6A4F; line-height:1.1;">—</div>
          <div style="font-size:10px; color:#bbb; margin-top:3px;">death-exp. prevented / $</div>
        </div>
        <div style="background:white; border:1px solid #e2e8f0; border-radius:8px; padding:12px; text-align:center;">
          <div style="font-size:10px; text-transform:uppercase; letter-spacing:0.5px; color:#888; margin-bottom:5px;">Suffering reduction</div>
          <div id="st-sr" style="font-size:22px; font-weight:800; color:#C44E52; line-height:1.1;">—</div>
          <div style="font-size:10px; color:#bbb; margin-top:3px;">vs. current pesticide</div>
        </div>
      </div>

      <!-- Attribution + Notes -->
      <div style="margin-top:12px; background:#f8f9fa; border:1px solid #e2e8f0; border-radius:8px; padding:11px 14px; font-size:11.5px; color:#555; line-height:1.7;">
        <div style="margin-bottom:5px;">
          📄 <strong>Based on:</strong>
          <a href="https://reducing-suffering.org/humane-insecticides/" target="_blank"
             style="color:#2D6A4F; font-weight:600; text-decoration:none;">
            Humane Insecticides
          </a>
          — Brian Tomasik, <em>Essays on Reducing Suffering</em>. Last updated: November 12, 2018.
        </div>
        <div>
          💻 <strong>Dashboard implementation:</strong> Solimary García-Hernández, for the <em>Fairer Fields</em> initiative · <a href="mailto:solimarygarcia@gmail.com" style="color:#2D6A4F; text-decoration:none;">solimarygarcia@gmail.com</a>
        </div>
        <div style="font-size:11px; color:#888;">
          <strong>⚠️ Model ignores:</strong> fixed research costs · administrative overhead · farmer outreach · compliance monitoring.
          MC priors: ln(<em>p</em>) ~ U[−6, −0.5] · ln(<em>n</em>) ~ N(15, 2) · <em>f</em> ~ N(0.8, 0.05) · <em>s</em> ~ U[0.3, 0.9] · <em>c</em> ~ U[$1, $8].
        </div>
      </div>

    </div>
  </div>
</div>

<script>
(function(){
  // ── Normal sample (Box-Muller) ──
  function randn(m,sd){
    var u=0,v=0;
    while(u===0) u=Math.random();
    while(v===0) v=Math.random();
    return m+sd*Math.sqrt(-2*Math.log(u))*Math.cos(2*Math.PI*v);
  }

  // ── Format numbers ──
  function fmt(x){
    if(x===undefined||isNaN(x)) return '—';
    if(x>=1e12) return (x/1e12).toFixed(2)+'T';
    if(x>=1e9)  return (x/1e9).toFixed(2)+'B';
    if(x>=1e6)  return (x/1e6).toFixed(2)+'M';
    if(x>=1e3)  return (x/1e3).toFixed(1)+'K';
    if(x>=1)    return x.toFixed(1);
    if(x>=0.001) return x.toFixed(4);
    return x.toExponential(2);
  }

  // ── Pre-generate MC samples (run once) ──
  var N=50000;
  var sp=[],sn=[],sf=[],ss=[],sc=[];
  for(var i=0;i<N;i++){
    sp.push(Math.exp(-6+Math.random()*5.5));
    sn.push(Math.exp(randn(15,2)));
    sf.push(Math.max(0.01,Math.min(0.99,randn(0.8,0.05))));
    ss.push(0.3+Math.random()*0.6);
    sc.push(1+Math.random()*7);
  }
  var mcR=sp.map(function(p,i){ return p*sn[i]*sf[i]*(1-ss[i])/sc[i]; });
  var mcLogR=mcR.map(function(r){ return Math.log10(Math.max(r,1e-6)); });
  var LO=Math.floor(Math.min.apply(null,mcLogR));
  var HI=Math.ceil(Math.max.apply(null,mcLogR));
  var NBINS=48;
  var bins=new Array(NBINS).fill(0);
  mcLogR.forEach(function(v){
    var idx=Math.floor((v-LO)/(HI-LO)*NBINS);
    idx=Math.max(0,Math.min(NBINS-1,idx));
    bins[idx]++;
  });
  var maxB=Math.max.apply(null,bins);
  var mcMeanLogR=mcLogR.reduce(function(a,b){return a+b;},0)/N;

  // ── Draw histogram ──
  function drawHist(peLR){
    var svg=document.getElementById('hist-svg');
    if(!svg) return;
    var W=svg.getBoundingClientRect().width||600;
    var H=170;
    var pl=44,pr=12,pt=10,pb=28;
    var cw=W-pl-pr, ch=H-pt-pb;
    var bw=cw/NBINS;
    var html='';

    // bars
    for(var i=0;i<NBINS;i++){
      var bh=(bins[i]/maxB)*ch;
      var x=pl+i*bw, y=pt+ch-bh;
      var lv=LO+(i+0.5)*(HI-LO)/NBINS;
      var col=lv<=peLR?'#74C69D':'#2D6A4F';
      html+='<rect x="'+x+'" y="'+y+'" width="'+(bw-0.5)+'" height="'+bh+'" fill="'+col+'" opacity="0.82"/>';
    }

    // axes
    html+='<line x1="'+pl+'" y1="'+(pt+ch)+'" x2="'+(pl+cw)+'" y2="'+(pt+ch)+'" stroke="#ddd" stroke-width="1"/>';
    html+='<line x1="'+pl+'" y1="'+pt+'" x2="'+pl+'" y2="'+(pt+ch)+'" stroke="#ddd" stroke-width="1"/>';

    // x ticks
    for(var t=LO;t<=HI;t++){
      var tx=pl+(t-LO)/(HI-LO)*cw;
      html+='<line x1="'+tx+'" y1="'+(pt+ch)+'" x2="'+tx+'" y2="'+(pt+ch+4)+'" stroke="#bbb" stroke-width="1"/>';
      html+='<text x="'+tx+'" y="'+(pt+ch+16)+'" text-anchor="middle" font-size="9" fill="#888">10<tspan dy="-4" font-size="7">'+t+'</tspan></text>';
    }

    // y label
    html+='<text x="10" y="'+(pt+ch/2)+'" text-anchor="middle" font-size="9" fill="#aaa" transform="rotate(-90,10,'+(pt+ch/2)+')">Frequency</text>';

    // MC mean line
    var mx=pl+(mcMeanLogR-LO)/(HI-LO)*cw;
    html+='<line x1="'+mx+'" y1="'+pt+'" x2="'+mx+'" y2="'+(pt+ch)+'" stroke="#F4A261" stroke-width="2" stroke-dasharray="5,3"/>';
    html+='<text x="'+(mx+4)+'" y="'+(pt+13)+'" font-size="9" fill="#F4A261">MC mean</text>';

    // Point estimate line
    var px=pl+(peLR-LO)/(HI-LO)*cw;
    px=Math.max(pl,Math.min(pl+cw,px));
    html+='<line x1="'+px+'" y1="'+pt+'" x2="'+px+'" y2="'+(pt+ch)+'" stroke="#C44E52" stroke-width="2.5"/>';
    var lblX=px+5>pl+cw-50?px-5:px+5;
    var anchor=px+5>pl+cw-50?'end':'start';
    html+='<text x="'+lblX+'" y="'+(pt+25)+'" text-anchor="'+anchor+'" font-size="9" fill="#C44E52" font-weight="600">Your estimate</text>';

    svg.innerHTML=html;
  }

  // ── Main update function ──
  function wSim(){
    var p  = parseFloat(document.getElementById('sl-p').value);
    var lnn= parseFloat(document.getElementById('sl-n').value);
    var n  = Math.exp(lnn);
    var f  = parseFloat(document.getElementById('sl-f').value);
    var s  = parseFloat(document.getElementById('sl-s').value);
    var c  = parseFloat(document.getElementById('sl-c').value);

    // Update labels
    document.getElementById('lbl-p').textContent = p.toFixed(3);
    document.getElementById('lbl-n').textContent = n>=1e6?(n/1e6).toFixed(1)+'M':(n/1e3).toFixed(0)+'K';
    document.getElementById('lbl-f').textContent = f.toFixed(2);
    document.getElementById('lbl-s').innerHTML   = s.toFixed(2)+' <span style="font-weight:400;color:#888;">('+Math.round((1-s)*100)+'% reduction)</span>';
    document.getElementById('lbl-c').textContent = '$'+c.toFixed(1);

    // R point estimate
    var R = p*n*f*(1-s)/c;

    // Update stat cards
    document.getElementById('st-R').textContent  = fmt(R);
    document.getElementById('st-sr').textContent = Math.round((1-s)*100)+'%';
    document.getElementById('formula-live').textContent = fmt(R);

    // ── Farmer plain-language translation ──
    var farmEl = document.getElementById('sl-farm');
    var farm_ha = farmEl ? Math.max(1, parseFloat(farmEl.value)||50) : 50;
    var insects_helped = p * n * f * (1 - s) * farm_ha;
    var subsidy_total  = c * farm_ha;
    var cost_per_1000  = 1000 / R;
    var reduction_pct  = Math.round((1-s)*100);
    var insects_per_ha = Math.round(p * n * f * (1-s));

    function fmtI(x){
      if(x>=1e9)  return (x/1e9).toFixed(1)+' billion';
      if(x>=1e6)  return (x/1e6).toFixed(1)+' million';
      if(x>=1e3)  return (x/1e3).toFixed(0)+' thousand';
      return Math.round(x).toString();
    }

    var farmerHTML =
      '<p style="margin:0 0 6px 0;">'+
        'On a <strong>'+farm_ha+'-hectare farm</strong>, switching to the more humane pesticide this season would spare roughly '+
        '<strong>'+fmtI(insects_helped)+' insects</strong> from a more painful death — about '+
        '<strong>'+fmtI(insects_per_ha)+' per hectare</strong>.'+
      '</p>'+
      '<p style="margin:0 0 6px 0;">'+
        'The pesticide switch is <strong>'+reduction_pct+'% less painful</strong> per unit of time, meaning insects die faster and suffer less overall. '+
        'Both pesticides kill roughly the same number of insects — only the experience of dying changes.'+
      '</p>'+
      '<p style="margin:0 0 6px 0;">'+
        'A subsidy program would pay you <strong>$'+subsidy_total.toFixed(0)+'</strong> per season to cover the extra cost ($'+c.toFixed(0)+'/hectare). '+
        'That works out to <strong>$'+fmt(cost_per_1000)+' per 1,000 insects helped</strong> — or put another way, '+
        'every dollar of subsidy benefits approximately <strong>'+fmtI(R)+' insects</strong>.'+
      '</p>'+
      '<p style="margin:0; color:#888; font-size:11px;">'+
        '⚠️ These numbers assume a probability of '+p.toFixed(3)+' that insects are sentient. '+
        'If insects do not feel pain (p = 0), the benefit is zero regardless of the pesticide used.'+
      '</p>';

    document.getElementById('farmer-text').innerHTML = farmerHTML;

    drawHist(Math.log10(Math.max(R,1e-6)));
  }

  // ── Reset to defaults ──
  function wReset(){
    document.getElementById('sl-p').value  = 0.1;
    document.getElementById('sl-n').value  = 15;
    document.getElementById('sl-f').value  = 0.8;
    document.getElementById('sl-s').value  = 0.5;
    document.getElementById('sl-c').value  = 4.5;
    wSim();
  }

  // Expose globally (called from oninput)
  window.wSim=wSim;
  window.wReset=wReset;

  // Init
  wSim();
  window.addEventListener('resize', function(){ wSim(); });
})();
</script>
```
